My english activity log

### 2019-10-20 english-activity.Rmd
jusqu'au 20/10/2019

>>>>

14/10/2019 : I read some articles for my presentation.

15/10/2019 : I read some articles for my presentation and I watched a documentary about coral bleaching https://www.youtube.com/watch?v=5cr8S5tTiz4.

16/10/2019 : I read some articles for my presentation.

17/10/2019 : I watched a video about the types of natural selection https://www.youtube.com/watch?v=DBPGLythma0.

19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU.

20/10/2019 : I watched a video about resting potential but it was said the opposite of what we were taught in class (so I don't put the link).
